2020 U.S. Presidential Election Forecast

### 2024-03-15 paper/paper.qmd
typo

This survey data is an 18-month election study conducted by UCLA researchers with roughly 6250 online interviews each from from July 2019 to February 2021 (@citeSurveyData). The sample is weighted to represent the U.S. adult population (@citeSurveyData). Nationscape groups weight on the following important factors: gender, the four major census regions, race, Hispanic ethnicity, household income, education, age, language spoken at home, nativity, 2016 presidential vote, and the urban-rural mix of the respondent's ZIP code (@citeSurveyData). According to the data, Male make up 48.3% while female make up 51.3% (@citeSurveyData). 74.2% of the respondents are White, 6.8% are Asian/Pacific, 12% are Black (@citeSurveyData). 20.4% are those between 18-29, 33.4% are 30-49, 32.4% are 50-69, 3.3% are 70+ (@citeSurveyData). On average, 5.1 percent declined immediately among those who are selected for the survey. 16.7 percent of the respondents did not complete the survey. Another 5.9 percent were categorized as speeding or straight-line which means they completed the survey in less than 6 minutes or selected the same response for every question in the three policy question batteries. Leaving these out leave 72.4 percent of the original sample for the analysis.

>>>>

This survey data is an 18-month election study conducted by UCLA researchers with roughly 6250 online interviews each from from July 2019 to February 2021 [@citeSurveyData]. The sample is weighted to represent the U.S. adult population [@citeSurveyData]. Nationscape groups weight on the following important factors: gender, the four major census regions, race, Hispanic ethnicity, household income, education, age, language spoken at home, nativity, 2016 presidential vote, and the urban-rural mix of the respondent's ZIP code [@citeSurveyData]. According to the data, Male make up 48.3% while female make up 51.3% [@citeSurveyData]. 74.2% of the respondents are White, 6.8% are Asian/Pacific, 12% are Black [@citeSurveyData]. 20.4% are those between 18-29, 33.4% are 30-49, 32.4% are 50-69, 3.3% are 70+ [@citeSurveyData]. On average, 5.1 percent declined immediately among those who are selected for the survey. 16.7 percent of the respondents did not complete the survey. Another 5.9 percent were categorized as speeding or straight-line which means they completed the survey in less than 6 minutes or selected the same response for every question in the three policy question batteries. Leaving these out leave 72.4 percent of the original sample for the analysis.
